Block bootstrap consistency\\under weak assumptions

### 2017-01-10 Paper.tex
[#34/abs] Remove some absolute value signs requested by referee

Lemma~\ref{L4} implies that
$\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
probability. This convergence then implies that
\begin{equation}
  \label{eq:23}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x\big] \to^p \Phi(x/\sigma)
\end{equation}
and
\begin{equation}
\label{eq:24}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) / \hat\sigma_n^{*}
  \leq x\big] \to^p \Phi(x)
\end{equation}
for any $x$.  These results are sufficient for~\eqref{eq:36}
and~\eqref{eq:2} since the limiting distribution is continuous,
a standard argument that proceeds as follows \citep[see][Lemma 2.11, for example]{Vaa:00}.
Let $k$ be a finite integer and define $x_i = \sigma \Phi^{-1}(i/k)$ for $i =
0,\dots,k$ (so $x_0 = -\infty$ and $x_k = +\infty$).
For any $x \in [x_i, x_{i+1}]$,
\begin{align*}
  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
  &\leq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_i/\sigma) \\
  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_{i+1}/\sigma) + 1/k
\intertext{and}
  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
  &\geq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_{i+1}/\sigma) \\
  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_i/\sigma) - 1/k
\end{align*}
almost surely. Then
\begin{multline*}
  \sup_{x \in (-\infty, +\infty)} \big| \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma) \big| \\
  \leq \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k
\end{multline*}
almost surely and~\eqref{eq:23} ensures that
\begin{equation*}
  \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n)
  \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k \to^p 1/k
\end{equation*}
for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
Theorem~\ref{T1}'s assumptions ensure that the original array obeys
the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.  A similar
argument applies to the asymptotic distribution of
$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
proof.\qed }

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, take $x$ to be an arbitrary positive number. Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq n x \Big]
    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
  \end{equation*}
  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
  by assumption, so
  \begin{align*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
    \to \exp(0) = 1.
  \end{align*}
  Since $x$ is arbitrary, this completes the proof.

>>>>

Lemma~\ref{L4} implies that
$\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
probability. This convergence then implies that
\begin{equation}
  \label{eq:23}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x\big] \to^p \Phi(x/\sigma)
\end{equation}
and
\begin{equation}
\label{eq:24}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) / \hat\sigma_n^{*}
  \leq x\big] \to^p \Phi(x)
\end{equation}
for any $x$.  These results are sufficient for~\eqref{eq:36}
and~\eqref{eq:2} though an argument attributed to Poly{\`a}
that proceeds as follows.
Let $k$ be a finite integer and define $x_i = \sigma \Phi^{-1}(i/k)$ for $i =
0,\dots,k$ (so $x_0 = -\infty$ and $x_k = +\infty$).
For any $x \in [x_i, x_{i+1}]$,
\begin{align*}
  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
  &\leq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_i/\sigma) \\
  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_{i+1}/\sigma) + 1/k
\intertext{and}
  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
  &\geq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_{i+1}/\sigma) \\
  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_i/\sigma) - 1/k
\end{align*}
almost surely. Then
\begin{multline*}
  \sup_{x \in (-\infty, +\infty)} \big| \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma) \big| \\
  \leq \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k
\end{multline*}
almost surely and~\eqref{eq:23} ensures that
\begin{equation*}
  \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n)
  \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k \to^p 1/k
\end{equation*}
for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
Theorem~\ref{T1}'s assumptions ensure that the original array obeys
the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.  A similar
argument applies to the asymptotic distribution of
$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
proof.\qed }

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, observe that, for any increasing positive sequence
  $x_n$ such that $x_n p_n \to \infty$,
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
  \end{equation*}
  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
  $x_n = n x$ for any positive number $x$.  Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
    \lim \exp(-C n p_n e^{-n p_n x}) =
    \exp(0) = 1.
  \end{equation*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
